---
title: Exploring a new data set
author: LAFerrat
date: '2020-07-03'
slug: Exploring-a-new-data-set
categories:
  - R
tags:
  - missing data
  - figures
  - graph
---
Beyond the classic functions like [summary()](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/summary), or [str()](https://www.rdocumentation.org/packages/utils/versions/3.6.2/topics/str) , there is a set of dedicated packages to explore a new dataset. In this post, I will describe three useful packages which give a good perspective on a new dataset.
The first one is [visdat](https://cran.r-project.org/web/packages/visdat/vignettes/using_visdat.html) which gives tools to visualise at one glance a new dataset. 

Its major functions are vis_dat,vis_miss and ,vis_cor
vis_dat takes litteraly "looking at the data". This is useful to identify pattern and potential biais in the data.
```{r}
library(visdat)
vis_dat(airquality)
```

vis_miss gives an insight about missing values 
```{r}
vis_miss(airquality)
```

vis_cor which give a quick look at the correlation between the variables
```{r}
vis_cor(airquality,
        na_action = "complete.obs")
```

For larger dataset, with more variables and/or a large number of observation I prefer to use [naniar](http://naniar.njtierney.com/articles/getting-started-w-naniar.html) which gives tools to visualise at one glance a large dataset and particularly focus on missing values. 
The function gg_miss_upset shows which variables are missing simultanously.
```{r}
library(naniar)
gg_miss_upset(airquality,nsets = 10)
```

Finally the package [DataExplorer](https://cran.r-project.org/web/packages/DataExplorer/vignettes/dataexplorer-intro.html) is a must. With one function a detailed report is generated with a large number of descriptive graphs. Including data structure, univariate distribution for each variables, QQ plot, correlation analysis, principal component analysis, 

```{r, warning= FALSE, eval=FALSE}
library(DataExplorer)
DataExplorer::create_report(airquality)
```

If one of variable is of particular interest, for example, Ozone, it i possible to indicate it and specific graphs to describe the relationship between this variable and the other variables will be drawn such as bivariate distribution, scatter plot...
```{r, warning= FALSE, eval=FALSE}
library(DataExplorer)
DataExplorer::create_report(airquality, y = "Ozone")
```